OSMAC_Method; Model: `r params$Model_Path`; 

### 2023-02-11 Identical_r0/Rmarkdown/r1_OSMAC_Method.Rmd
MSE for MLE added to the rmarkdown files and updated

# OSMAC ;  Response Model : `r params$Model_Path`

@@

```{r Load Data}
Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","Real_Model/")
load(here(Path,"OSMAC_output.RData"))

@@

```{r Load Data Assumed Models}
Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model/")
# Assumed Model 1
load(here(Path,"OSMAC_output_Old_1.RData"))

@@

# Assumed Model 2
load(here(Path,"OSMAC_output_Old_2.RData"))

@@

load(here(Path,"OSMAC_output_Old_3.RData"))

@@

```{r Load Data Assumed Models 2}
Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model/")
# Assumed Model 1
load(here(Path,"OSMAC_output_New_1.RData"))

@@

# Assumed Model 2
load(here(Path,"OSMAC_output_New_2.RData"))

@@

# Assumed Model 3
load(here(Path,"OSMAC_output_New_3.RData"))

@@

```{r Load Data Model Free}
Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","ModelFree/")
load(here(Path,"OSMAC_output.RData"))

@@

anim_save(filename="para_1.gif",animation = para_1,
          path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","para_1.gif"))
```

@@

anim_save(filename="Bias_1.gif",animation = Bias_1,
          path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","Bias_1.gif"))
```

@@

anim_save(filename="U_1.gif",animation = U_1,
          path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","U_1.gif"))

@@

anim_save(filename="U_2.gif",animation = U_2,
          path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","U_2.gif"))
```

@@

# Store the Results
save(All_MSE,All_MSE_MLE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
     file = here("Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
                 "No_Correlated_Covariate_OSMAC.RData"))
```

>>>>

# Different r0 values; OSMAC ;  Response Model : `r params$Model_Path`

@@

```{r Load Data}
Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","Real_Model/")
load(here(Path,"OSMAC_output_r1.RData"))

@@

```{r Load Data Assumed Models}
Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model/")
# Assumed Model 1
load(here(Path,"OSMAC_output_Old_1_r1.RData"))

@@

# Assumed Model 2
load(here(Path,"OSMAC_output_Old_2_r1.RData"))

@@

load(here(Path,"OSMAC_output_Old_3_r1.RData"))

@@

```{r Load Data Assumed Models 2}
Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model/")
# Assumed Model 1
load(here(Path,"OSMAC_output_New_1_r1.RData"))

@@

# Assumed Model 2
load(here(Path,"OSMAC_output_New_2_r1.RData"))

@@

# Assumed Model 3
load(here(Path,"OSMAC_output_New_3_r1.RData"))

@@

```{r Load Data Model Free}
Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","ModelFree/")
load(here(Path,"OSMAC_output_r1.RData"))

@@

anim_save(filename="r1_para_1.gif",animation = para_1,
          path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","r1_para_1.gif"))
```

@@

anim_save(filename="r1_Bias_1.gif",animation = Bias_1,
          path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","r1_Bias_1.gif"))
```

@@

anim_save(filename="r1_U_1.gif",animation = U_1,
          path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","r1_U_1.gif"))

@@

anim_save(filename="r1_U_2.gif",animation = U_2,
          path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","r1_U_2.gif"))
```

@@

# Store the Results
save(All_MSE,All_MSE_MLE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
     file = here("Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
                 "No_Correlated_Covariate_OSMAC_r1.RData"))
```
